Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-07 docs/evol.tex
Add discussion on diffs

>>>>

Another take on this theme is shown in Figure~\ref{fig:bugddifs},
which presents an histogram of the changes of different bug counts in
project versions. In most cases, a bug count does not change between
versions; but when it does change, it may change upwards or downwards.
Note also the spectacular changes of introducing or removing thousands
of defects; this may be the result of doing and undoing a pervasive
code change that falls foul of some bug identification rule.

\begin{figure*}
  \centering
  \includegraphics[scale=0.4]{bugdiffs}
  \caption{Histograms of the time, measure in versions, it takes for a
    bug to be closed. }
  \label{fig:bugdiffs}
\end{figure*}
